\section{Related work}

\paragraph{ODE-based sampling.}
ODE-based samplers are much more widely used in practice \cite{stablediffusion} than SDE-based methods because they can take large time steps by leveraging some useful structures of the underlying ODE such as semi-linear structure and the form of exponentially weighted integral \cite{lu2022dpm, zhang2022fast}. Existing works \cite{song2021denoising, bao2021analytic, zhang2022fast,dockhorn2022genie} have greatly reduced the number of discretization steps to 10-50 in time while keeping the approximation error small to generate high-quality samples. The exponentially weighted integral structure of the solution trajectory revealed by prior works also inspired our design of the temporal convolution block. 
% We note that these advanced numerical solvers allow us to approximate the solution operator with less computation cost, which greatly speeds up our training data generation process and also benefits other training-based methods.  
 % In this paper, we also use some of the advanced ODE-based solvers to generate our training set for DSNO. 
\vspace{-0.1in}
\paragraph{Operator learning for solving PDEs.}
Neural operators are deep learning models that are designed for mappings between function spaces, i.e., continuous functions~\cite{li2020neural,kovachki2021universal}. They are widely deployed as the de facto deep learning models in scientific computing when dealing with partial differential equations (PDE).
% Operator learning is a successful learning paradigm in the scientific computing area for solving partial differential equations. It contains a diverse class of methods including DeepOnet-based methods and neural operator methods including \citet{li2020neural, li2020multipole, li2020fourier}. 
Among these methods, Fourier neural operator stands out and is one of the most efficient machine learning methods for scientific computing problems involving PDE
\cite{yang2021seismic,wen2022accelerating}. It is shown to possess the crucial discretization invariance and universal approximation properties of universal operators~\citep{kovachki2021universal,kovachki2021neural}, which motivates our design of the temporal convolution block in our method.


\vspace{-0.1in}
\paragraph{Training-based sampling.} Training-based methods typically train a neural network surrogate to replace some parts of the numerical solver or even the whole solver. This category includes various methods from diverse perspectives such as knowledge distillation \cite{luhman2021knowledge, salimans2021progressive}, learning the noise schedule \cite{lam2021bilateral, watson2021learning}, learning the reverse covariance \cite{bao2022estimating}, which require extra training. Training-based methods usually work in the few-step regime with less than 10 steps. Direct \citet{luhman2021knowledge} is the first work to get descent sample quality on CIFAR10 with one model evaluation but it suffers from overfitting and its sampling quality drops dramatically compared to the original sampling methods of diffusion models. The current SOTA progressive distillation \cite{salimans2021progressive} reduces the number of steps down to 4-8 without losing much sample quality. However, it has the same issue as knowledge distillation in the limit of one function evaluation. Some other methods~\cite{xiao2021tackling,vahdat2021score, zheng2022truncated} combine diffusion models with other generative models such as GAN and VAE to enable fast sampling. 
% For example, DDGAN \cite{xiao2021tackling} achieves excellent FID scores with as few as 4 steps by leveraging conditional GAN to model the denoising distributions or equivalently the reverse stochastic process, allowing for large denoising steps. But it involves adversarial training like GAN does which can be potentially harder to train than the methods that directly utilize the pre-trained diffusion models. LSGM \cite{vahdat2021score} greatly accelerates sampling by learning an encoder that transforms the data distribution into a smooth latent distribution that is close to a Gaussian prior so that the reverse process is smooth and allows for large time steps. LSGM requires 20 to 100 steps to generate reasonable samples. 
% \paragraph{Parallel decoding.} Parallel decoding is mainly used for the discrete tokens in the language models~\cite{ghazvininejad2019mask} and vision transformers~\cite{chang2023muse}, which can predict multiple tokens with only one model forward pass. 

