

The classical development of neural networks has primarily focused on learning mappings between finite dimensional Euclidean spaces or finite sets.
We propose a generalization of neural networks to learn operators, termed \emph{neural operators}, that map between infinite dimensional function spaces.
We formulate the neural operator as a composition of  linear integral operators and nonlinear activation functions. We prove a universal approximation theorem for our proposed neural operator, showing that it can approximate any given nonlinear continuous operator. The proposed neural operators are also discretization-invariant, i.e., they share the same model parameters among different discretization of the underlying function spaces. 
Furthermore, we introduce four classes of efficient parameterization, viz., graph neural operators,  multi-pole graph neural operators, low-rank neural operators, and Fourier neural operators.
An important application for neural operators is learning surrogate maps for the solution operators of
partial differential equations (PDEs). We consider standard PDEs such as the Burgers, Darcy subsurface flow, and the Navier-Stokes equations, and show that the proposed neural operators have superior performance compared to existing machine learning based methodologies,
while being several orders of magnitude faster than conventional PDE solvers. 

%Numerical experiments are presented in which the solution operator (mapping initial condition to solution)  is learned for Burgers' equation and the Navier-Stokes equation, and in which the coefficient to solution map is learned in the Darcy model of porous medium flow; a variety of linear operators, defined by linear  PDEs, are also used to illustrate key ideas.



% \kamyar{
% The classical development of neural networks has been primarily for mappings between a finite-dimensional spaces, e.g., between Euclidean space and a set of classes/labels, or between two finite-dimensional Euclidean spaces.
% The purpose of this work is to generalize neural networks so that they can learn operators mapping between general spaces, e.g., between infinite dimensional spaces, such as function spaces. 
% We formulate the approximation of operators by composition of nonlinear local activation functions and a class of linear local and non-local integral operators, so that the composed operator can approximate complex nonlinear, local, and non-local operators.
% In this paper, we propose four formulations of the integral operators: graph-based operators, multipole graph-based operators, low rank operators, and Fourier operators.
% Experiments confirm that the proposed neural operators have the desirable resolution-invariant properties and show competitive performance compared to existing methodologies from both the fields of neural networks and numerical analysis. }